MinCall --- MinION end2end deep learning basecaller

### 2017-07-01 paper/main.tex
Replaced "base call" with basecall

In Appendix~\ref{app:evaluation:CIGAR} the histogram figure~\ref{fg:cigar_op_dist} shows how matches, mismatches, insertions, and deletions are distributed across the reads. It is shown that mismatches and insertion occur more frequently at the beginnings and the ends of the reads. This is not only the case for the developed basecaller, but all other show the same property. This could be due to lack of context information from both sides when edges are base called.

@@

Currently, without support for newer sequencing data, this model has limited application. It can be used as a demonstration of a different approach to base calling which yields promising results.  As newer versions of basecallers by Oxford Nanopore do not offer any support for data sequenced with the previous version of chemistries, this tool can be used to re-basecall that data and improvement of the quality of reads retrospectively.

@@

\subsection{Official}
\emph{Metrichor} is an Oxford Nanopore company that offers cloud-based platform \emph{EPI2ME} for analysis of nanopore data.
Initially, base calling was only available by uploading data to the platform - that being the reason why this basecaller is often called Metrichor even though it is a name of the company.

@@

\emph{Scrappie}\footnote{\url{https://github.com/nanoporetech/scrappie}} is another basecaller by Oxford Nanopore Technologies. Similar to Nanonet, it is the platform for ongoing development. Scrappie is reported to be the first basecaller  that specifically address homopolymer base calling. It became publicly available just recently in June, 2017 and supports R9.4 and future R9.5 data.

>>>>

In Appendix~\ref{app:evaluation:CIGAR} the histogram figure~\ref{fg:cigar_op_dist} shows how matches, mismatches, insertions, and deletions are distributed across the reads. It is shown that mismatches and insertion occur more frequently at the beginnings and the ends of the reads. This is not only the case for the developed basecaller, but all other show the same property. This could be due to lack of context information from both sides when edges are basecalled.

@@

Currently, without support for newer sequencing data, this model has limited application. It can be used as a demonstration of a different approach to basecalling which yields promising results.  As newer versions of basecallers by Oxford Nanopore do not offer any support for data sequenced with the previous version of chemistries, this tool can be used to re-basecall that data and improvement of the quality of reads retrospectively.

@@

\subsection{Official}
\emph{Metrichor} is an Oxford Nanopore company that offers cloud-based platform \emph{EPI2ME} for analysis of nanopore data.
Initially, basecalling was only available by uploading data to the platform - that being the reason why this basecaller is often called Metrichor even though it is a name of the company.

@@

\emph{Scrappie}\footnote{\url{https://github.com/nanoporetech/scrappie}} is another basecaller by Oxford Nanopore Technologies. Similar to Nanonet, it is the platform for ongoing development. Scrappie is reported to be the first basecaller  that specifically address homopolymer basecalling. It became publicly available just recently in June, 2017 and supports R9.4 and future R9.5 data.
